\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
Noise Contrastive Estimation (NCE) and Hierarchical Softmax

\usepackage{url}

@@

\subparagraph{Negative Sampling}

>>>>

\usepackage{url}
\usepackage{amsmath}

@@

For any inner node $n$, let $mid(n)$ be an arbitrary fixed child of $n$, and define $\| x \|$ as
\[ \begin{cases} 
      0 & x \ is \  false\\
      1 & x \ is \ true
   \end{cases}
\]
Then we define \textbf{Hierarchical Softmax} $p(w_O | w_I)$ as follows
p(w_O | w_I) = \prod^{L(w)-1}_{j = 1} \sigma ( \| n(w, j + 1) = mid(n(w, j))\| x_{n(w, j)}^{T} v_{w_j} )
where $\sigma$ is defined as
\sigma(x) = \frac{1}{1 + exp(-x)}
Also
\sum^W_{w = 1} p(w | w_I) = 1
The above fomulas indicates that the computational cost is proportional to $L(w_O)$, which on average is smaller than $logW$.
\subparagraph{Negative Sampling} This model has another name called \textbf{Noise Contrastive Estimation (NCE)}
